Load Libraries
```{r}
library(dplyr)
library(ggplot2)
library(lubridate)
library(stringr)
```


1. Data Preprocessing
```{r }
data_movies=read.csv("ml-latest-small/movies.csv")
data_ratings=read.csv("ml-latest-small/ratings.csv")
data_moviesRatings=inner_join(data_movies, data_ratings, by='movieId')

#Transform Timestamp to Date
data_moviesRatings=mutate(data_moviesRatings,timestamp=as.POSIXct(data_moviesRatings[,6], tz='UTC', origin='1970-01-01'))

# Add Day Month and Year variable in the main data
data_moviesRatings=data_moviesRatings%>%
mutate(Year=year(timestamp), Day=day(timestamp), Month=month(timestamp,label=TRUE), Hour=hour(timestamp), Week=wday(timestamp, label=TRUE))

data_moviesRatings$Hour[data_moviesRatings$Hour == 0] <- 24

str(data_moviesRatings)

```

Q1.1 - The distribution of ratings per movie (i.e. how many ratings are there per movie?).

```{r}
#------------------------------------------------------------------------------------    

                  # 1. RATINGS BY MOVIE from 1995 - 2016
    
    Q1.1_ratingsByMovie=data_moviesRatings%>%
    group_by(movieId)%>%
    summarise(ratingsByMovie=n())%>%
    arrange(desc(ratingsByMovie))%>%
    transform(cumMovie = cumsum(ratingsByMovie),propMovieRatings=round(ratingsByMovie/sum(ratingsByMovie),digits=4))
      
    Q1.1_ratingsByMovie$freqMovie<-seq.int(nrow(Q1.1_ratingsByMovie))
    
    # Plot distribution of cumulative ratings by Movie
    ggplot(Q1.1_ratingsByMovie, 
          aes(freqMovie,cumMovie)) + 
          geom_line() +
          xlab("Movies Added") +
          ylab("Cummulative Ratings") +
          ggtitle("Growth of ratings with addition of movies") +
          theme(panel.background = element_blank())+
          labs(caption = "b) Growth of ratings with movies \n from 1995 - 2016")
    

      
    # Plot distribution of ratings over time
    ggplot(Q1.1_ratingsByMovie,aes(movieId,ratingsByMovie)) + 
      geom_line() +
      theme(panel.background = element_blank())+
      ylim(c(1,400))+
      xlab("Movie Id") +
      ylab("Total number of ratings received") +
      ggtitle("Distribution of ratings / movie")+    labs(caption = "a) Distribution of ratings / movie \n from 1995 - 2016")
    
        
#------------------------------------------------------------------------------------    

                                  # 2. CHRISTMAS
    
ratingsChristmas=data_moviesRatings[ data_moviesRatings$Day>25 & data_moviesRatings$Month<12,]%>%
    group_by(movieId)%>%
    summarise(ratingsByMovie=n())%>%
    arrange(movieId)

    # Plot distribution of ratings over Christmas
    ggplot(ratingsChristmas,
          aes(movieId,ratingsByMovie)) + 
          geom_line() +
          theme(panel.background = element_blank())+
          ylim(c(1,400))+
          xlab("Movie Id") +
          ylab("Total number of ratings received") +
          ggtitle("Distribution of ratings / movie from 1995 - 2016 \n over Xmas")+    labs(caption = "b) Movie ratings on Xmas from 1995 - 2016")
    
#------------------------------------------------------------------------------------    
                        
                          # 3. WEEKDAYS EXCLUDING XMAS
    
ratingsWeekdays=data_moviesRatings[ data_moviesRatings$Week<6 & !(data_moviesRatings$Day==25 & data_moviesRatings$Month==12),]
ratingsWeekdays=data_moviesRatings[ data_moviesRatings$Week<6 & !(data_moviesRatings$Day==25 & data_moviesRatings$Month==12),]%>%
    group_by(movieId)%>%
    summarise(ratingsByMovie=n())%>%
    arrange(movieId)


    # Plot distribution of ratings over weekdays
    ggplot(ratingsWeekdays,
          aes(movieId,ratingsByMovie)) + 
          geom_line() +
          theme(panel.background = element_blank())+
          ylim(c(1,400))+
          xlab("Movie Id") +
          ylab("Total number of ratings received") +
          ggtitle("Distribution of ratings / movie from 1995 - 2016 \n over weekdays excluding Xmas")+labs(caption = "a) Movie ratings from 1995 - 2016 on \n weekdays excluding Xmas")
    
    
    
    
  
#------------------------------------------------------------------------------------    

                          # 4. WEEKEND EXCLUDING XMAS
 
     ratingsWeekend=data_moviesRatings[ data_moviesRatings$Week>5& !(data_moviesRatings$Day==25 & data_moviesRatings$Month==12),]%>%
    group_by(movieId)%>%
    summarise(ratingsByMovie=n())%>%
    arrange(movieId)


    # Plot distribution of ratings over weekend
    ggplot(ratingsWeekend,
          aes(movieId,ratingsByMovie)) + 
          geom_line()  +
          theme(panel.background = element_blank())+
          ylim(c(1,400))+
          xlab("Movie Id") +
          ylab("Total number of ratings received") +
          ggtitle("Distribution of ratings / movie from 1995 - 2016 \n over weekends excluding Xmas")+ labs(caption = "")+labs(caption = "b) Movie ratings from 1995 - 2016 on \n weekends excluding Xmas")
    
    
#------------------------------------------------------------------------------------    
                        
                  # Misc. Analysis on WEEKDAYS & WEEKEND pattern
  #ratings2005
    
    ratings2005=data_moviesRatings[ 
  data_moviesRatings$Year==2005 & data_moviesRatings$Month<7,]%>%
    group_by(movieId)%>%
    summarise(ratingsByMovie=n())%>%
    arrange(movieId)

    
    
#ratingsWeekdaysAnalysis
  ratingsWeekdaysAnalysis=data_moviesRatings[ 
  data_moviesRatings$Week<6 & data_moviesRatings$Year==2005 & data_moviesRatings$Month<7,]%>%
    group_by(movieId)%>%
    summarise(ratingsByMovie=n())%>%
    arrange(movieId)


    # Plot distribution of ratings over weekdays
    ggplot(ratingsWeekdaysAnalysis,
          aes(movieId,ratingsByMovie)) + 
          geom_line() +
          theme(panel.background = element_blank())+
          ylim(c(1,15))+
          xlab("Movie Id") +
          ylab("Total number of ratings received") +
          ggtitle("Distribution of ratings / movie \n over weekdays in first half - 2005")+labs(caption = "a) Movie ratings for first 6 months \n 2005 weekdays")
    
#ratingsWeekendAnalysis
  ratingsweekendAnalysis=data_moviesRatings[ 
  data_moviesRatings$Week>5 & data_moviesRatings$Year==2005 & data_moviesRatings$Month<7,]%>%
    group_by(movieId)%>%
    summarise(ratingsByMovie=n())%>%
    arrange(movieId)


    # Plot distribution of ratings over weekdays
    ggplot(ratingsweekendAnalysis,
          aes(movieId,ratingsByMovie)) + 
          geom_line() +
          theme(panel.background = element_blank())+
          ylim(c(1,15))+
          xlab("Movie Id") +
          ylab("Total number of ratings received") +
          ggtitle("Distribution of ratings / movie \n over weekend in first half - 2005") +labs(caption = "a) Movie ratings for first 6 months \n 2005 weekends")
    
  

    
# Analysis Report

# For first half 2005
sum(ratingsWeekdaysAnalysis$ratingsByMovie)/sum(ratingsweekendAnalysis$ratingsByMovie)
sum(ratingsWeekdaysAnalysis$ratingsByMovie)/sum(ratings2005$ratingsByMovie)*100
sum(ratingsweekendAnalysis$ratingsByMovie)/sum(ratings2005$ratingsByMovie)*100


# From 1996 to 2016
sum(ratingsWeekdays$ratingsByMovie)/sum(ratingsWeekend$ratingsByMovie)
sum(ratingsWeekend$ratingsByMovie)/sum(Q1.1_ratingsByMovie$ratingsByMovie)*100
sum(ratingsWeekdays$ratingsByMovie)/sum(Q1.1_ratingsByMovie$ratingsByMovie)*100
sum(ratingsChristmas$ratingsByMovie)/sum(Q1.1_ratingsByMovie$ratingsByMovie)*100

```

Popular Movie Analysis
```{r}
    
        # AllTime Favouite (Most watched)
    AllTimeFav=data_moviesRatings%>%
    group_by(title)%>%
    summarise(ratingsByMovie=n(),avgRatingScore=mean(rating))%>%
    arrange(desc(ratingsByMovie))

    mostWatchedAllTimefav=head(AllTimeFav,6)     


   # WeekendDatabase (Most watched)
    movieWeekendDatabase=data_moviesRatings[data_moviesRatings$Week>5,]%>%
    group_by(title)%>%
    summarise(ratingsByMovie=n(),avgRatingScore=mean(rating))%>%
    arrange(desc(ratingsByMovie))

    mostWatchedWeekendDatabase=head(movieWeekendDatabase,15)

   
        # WeekdayDatabase (Most watched)
    movieWeekdayDatabase=data_moviesRatings[data_moviesRatings$Week<6,]%>%
    group_by(title)%>%
    summarise(ratingsByMovie=n(),avgRatingScore=mean(rating))%>%
    arrange(desc(ratingsByMovie))

    mostWatchedWeekdayDatabase=head(movieWeekdayDatabase,15)
    
    

```

Q1.2_ratingsByUser
User database Growth
```{r}

# Users

# Analysis on impact on ratings with the growth of User database    
Q1.2_ratingsByUser=data_moviesRatings%>%
      group_by(userId)%>%
      summarise(ratingsByUser=length(rating))%>%
      transform(cumUser = cumsum(ratingsByUser),propUserRatings=round(ratingsByUser/sum(ratingsByUser),digits=4))
      
    Q1.2_ratingsByUser$freqUsers<-seq.int(nrow(Q1.2_ratingsByUser))

    
    # Plot distribution of ratings over time
    ggplot(Q1.2_ratingsByUser, 
          aes(userId,ratingsByUser)) + 
          geom_line() +
          xlab("User Id") +
          ylab("Total number of ratings given") +
          ggtitle("Distribution of ratings / user") +
          theme(panel.background = element_blank())+
          labs(caption = "a) Distribution of ratings / user \n from 1995 - 2016")
    
    # Plot distribution of cumulative ratings by users
    ggplot(Q1.2_ratingsByUser, 
          aes(freqUsers,cumUser)) + 
          geom_line() +
          xlab("Users") +
          ylab("Cummulative Ratings") +
          ggtitle("Growth of ratings with addition of users") +
          theme(panel.background = element_blank())+
          labs(caption = "b) Growth of ratings with users \n from 1995 - 2016")

```
Q1.3 Ratings produced over time

```{r}
# Calculate ratings per day
Q1.3_ratingsOverTime=data_moviesRatings%>%
  group_by(Year,Month,Day)%>%
  summarise(ratingsByDay=length(rating),users=length(userId))%>%
  transform(cumFreqDay = frequency(Day),cumFreqRating = cumsum(ratingsByDay),cumUser=cumsum(users))

    
Q1.3_ratingsOverTime$freqDay<-seq.int(nrow(Q1.3_ratingsOverTime))

# Plot distribution of ratings over time
ggplot(Q1.3_ratingsOverTime, 
      aes(freqDay,ratingsByDay)) + 
      geom_line() +
      xlab("Days") +
      ylab("Ratings given / day") +
      ggtitle("Distribution of ratings over time")+
          theme(panel.background = element_blank())+
          labs(caption = "a) Distribution of ratings / day \n from 1995 - 2016")

# Plot distribution of cumulative ratings over time
ggplot(Q1.3_ratingsOverTime, 
      aes(freqDay,cumFreqRating)) + 
      geom_line() +
      xlab("Days") +
      ylab("Cumulative Ratings") +
      ggtitle("Growth of ratings over time")+
      theme(panel.background = element_blank())+
          labs(caption = "b) Cummulative ratings over time \n from 1995 - 2016")

```


Q2. In order to assess the mood of the user base, explore how the average rating score per day changes over time.


```{r}
# Calculate ratings per day from 1995-2016
Q2_ratingsOverTime=data_moviesRatings%>%
  group_by(Year,Month,Day)%>%
  arrange(Year,Month,Day)%>%
  summarise(avgRatingsByDay=mean(rating))%>%
  transform(cumAvg=mean(avgRatingsByDay))
Q2_ratingsOverTime$freqDay<-seq.int(nrow(Q2_ratingsOverTime))

# Plot distribution of cumulative ratings from 1995-2016
ggplot(Q2_ratingsOverTime, 
      aes(freqDay,avgRatingsByDay)) + 
      geom_line() +
      xlab("Days") +
      ylab("Average Rating Score / Day") +
      ggtitle("Average rating score over time")+
      theme(panel.background = element_blank())+
          labs(caption = "")

# Calculate ratings per days (in a month)
Q2_ratingsOverTimeDay=data_moviesRatings%>%
  group_by(Day)%>%
  arrange(Day)%>%
  summarise(avgRatingsByDay=mean(rating))%>%
  transform(cumAvg=mean(avgRatingsByDay))


# Plot distribution of cumulative ratings over a month
ggplot(Q2_ratingsOverTimeDay, 
      aes(Day,avgRatingsByDay)) + 
      geom_line() +
      xlab("Days") +
      ylab("Average Rating Score / Day") +
      ylim(1,5)+
      xlim(1,31)+
      ggtitle("Average rating score / days in a month")+
      theme(panel.background = element_blank())+
          labs(caption = "")



# Calculate ratings per days (in a week)
Q2_ratingsOverTimeWeek=data_moviesRatings%>%
  group_by(Week)%>%
  arrange(Week)%>%
  summarise(avgRatingsByWeek=mean(rating))%>%
  transform(cumAvg=mean(avgRatingsByWeek))


# Plot distribution of cumulative ratings over week
ggplot(Q2_ratingsOverTimeWeek, 
      aes(Week,avgRatingsByWeek)) + 
      geom_line() +
      xlab("Week") +
      ylab("Average Rating Score / Week") +
      ylim(1,5)+
      xlim(1,7)+
      ggtitle("Average rating score / week")+
      theme(panel.background = element_blank())+
          labs(caption = "")




# Calculate ratings per month
Q2_ratingsOverTimeMonth=data_moviesRatings%>%
  group_by(Month)%>%
  arrange(Month)%>%
  summarise(avgRatingsByMonth=mean(rating))%>%
  transform(cumAvg=mean(avgRatingsByMonth))


# Plot distribution of cumulative ratings per month
ggplot(Q2_ratingsOverTimeMonth, 
      aes(Month,avgRatingsByMonth)) + 
      geom_line() +
      xlab("Months") +
      ylab("Average Rating Score / Month") +
      ylim(1,5)+
      xlim(1,12)+
      ggtitle("Average rating score/ month")+
      theme(panel.background = element_blank())+
          labs(caption = "")


```



Q2. In order to assess the mood of the user base, explore how the average rating score per day changes over time.


```{r}
Hour=data_moviesRatings%>%
  group_by(Hour,Day,Week,Month, Year)%>%
  summarise(ratingsByHour=mean(rating))

boxplot(ratingsByHour~Hour, data=Hour, xlab="Hour", ylab="RatingScore",las=2, main="Average Rating Score by Hour",ylim=c(1,5))


Week=data_moviesRatings%>%
  group_by(Week,Month, Year)%>%
  summarise(ratingsByWeek=mean(rating))

boxplot(ratingsByWeek~Week, data=Week, xlab="Day of the Week", ylab="Average RatingScore",las=2, main="Average Rating Score by Week", ylim=c(1,5))


Month=data_moviesRatings%>%
  group_by(Month, Year)%>%
  summarise(ratingsByMonth=mean(rating))

boxplot(ratingsByMonth~Month, data=Month, xlab="Month", ylab="Average RatingScore",las=2, main="Average Rating Score by Month", ylim=c(1,5))


Year=data_moviesRatings%>%
  group_by(Day,Year)%>%
  summarise(ratingsByYear=mean(rating))

boxplot(ratingsByYear~Year, data=Year, xlab="Year", ylab="Average RatingScore",las=2, main="Average Rating Score by Year", ylim=c(1,5))


Day=data_moviesRatings%>%
  group_by(Month,Day)%>%
  summarise(ratingsByday=mean(rating))

boxplot(ratingsByday~Day, data=Day, xlab="Day of the month", ylab="Average RatingScore",las=2, main="Average Rating Score by Day", ylim=c(1,5))
```



Q2. In order to assess the mood of the user base, explore how the average rating score per day changes over time.


```{r}


Total=data_moviesRatings%>%
  group_by(userId,Year,Month,Day,Week,Hour)%>%
  arrange(Year,Month,Day,Week,Hour)%>%
  summarise(rating=length(rating))

HourRating=Total%>%
  group_by(Day,Hour)%>%
  summarise(ratingsByHour=mean(rating))

boxplot(ratingsByHour~Hour, data=HourRating, xlab="Hour", ylab="RatingScore",las=2, main="Rating by Hour")


WeekRating=Total%>%
  group_by(Day,Week)%>%
  summarise(ratingsByWeek=mean(rating))

boxplot(ratingsByWeek~Week, data=WeekRating, xlab="Day of the Week", ylab="Average RatingScore",las=2, main="Rating by Week")


MonthRating=Total%>%
  group_by(Day,Month)%>%
  summarise(ratingsByMonth=mean(rating))

boxplot(ratingsByMonth~Month, data=MonthRating, xlab="Month", ylab="Average RatingScore",las=2, main="Rating by Month")


YearRating=Total%>%
  group_by(Day,Year)%>%
  summarise(ratingsByYear=mean(rating))

boxplot(ratingsByYear~Year, data=YearRating, xlab="Year", ylab="Average RatingScore",las=2, main="Rating by Year")


DayRating=Total%>%
  group_by(Month,Day)%>%
  summarise(ratingsByday=mean(rating))

boxplot(ratingsByday~Day, data=DayRating, xlab="Day of the month", ylab="Average RatingScore",las=2, main="Rating by Day")

```


Q3.What are the top-5 and bottom-5 rated movies, based on their average scores, that have at least 25 ratings?
```{r}
Q3.0_avgRatingByMovie=data_moviesRatings%>%
  group_by(title)%>%
  summarise(avgRatingByMovie=
              round(mean(rating),digits=2), totalRatingByMovie=length(rating))%>%
              filter(totalRatingByMovie>25)%>%
              arrange(desc(avgRatingByMovie))

Q3.1_top5Movies=head(Q3.0_avgRatingByMovie,5)
Q3.2_bottom5Movies=tail(Q3.0_avgRatingByMovie,5)

```


Genre

```{r}
install.packages('splitstackshape')
library(splitstackshape)
Genre=data_moviesRatings%>%
  group_by(genres, Year,Month,Week,Day)%>%
  summarise(ratings=mean(rating))
Genre <- Genre %>% filter(!((genres=="(no genres listed)")))
GenreSplit=cSplit(Genre, "genres", "|")

GenreWorksheet2=GenreSplit%>% filter(!((genres_02=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_02)%>% rename(c('genres_02'='genres'))
GenreWorksheet3=GenreSplit%>% filter(!((genres_03=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_03)%>% rename(c('genres_03'='genres'))
GenreWorksheet4=GenreSplit%>% filter(!((genres_04=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_04)%>% rename(c('genres_04'='genres'))
GenreWorksheet5=GenreSplit%>% filter(!((genres_05=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_05)%>% rename(c('genres_05'='genres'))
GenreWorksheet6=GenreSplit%>% filter(!((genres_06=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_06)%>% rename(c('genres_06'='genres'))
GenreWorksheet7=GenreSplit%>% filter(!((genres_07=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_07)%>% rename(c('genres_07'='genres'))
GenreWorksheet8=GenreSplit%>% filter(!((genres_08=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_08)%>% rename(c('genres_08'='genres'))
GenreWorksheet9=GenreSplit%>% filter(!((genres_09=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_09)%>% rename(c('genres_09'='genres'))
GenreWorksheet10=GenreSplit%>% filter(!((genres_10=="NA")))%>% select(Year,Month,Week,Day,ratings,genres_10)%>% rename(c('genres_10'='genres'))



GenreMerge=  do.call("rbind", list(GenreWorksheet2, GenreWorksheet3,GenreWorksheet4,GenreWorksheet5,GenreWorksheet6,GenreWorksheet7,GenreWorksheet8,GenreWorksheet9,GenreWorksheet10))

GenreMerge=as.data.frame(GenreMerge)
class(GenreMerge)
```


```{r}
DayGenre=GenreMerge%>%
  group_by(genres,Day)%>%
  summarise(ratingsByDay=mean(ratings))

boxplot(ratingsByDay~genres, data=DayGenre,ylab="RatingScore/Day",las=2, main="Average Rating Score by Day",ylim=c(1,5))


YearGenre=GenreMerge%>%
  group_by(genres,Year)%>%
  summarise(ratingsByYear=mean(ratings))

boxplot(ratingsByYear~genres, data=YearGenre, ylab="RatingScore/Year",las=2, main="Average Rating Score by Year",ylim=c(1,5))

MonthGenre=GenreMerge%>%
  group_by(genres,Month)%>%
  summarise(ratingsByMonth=mean(ratings))

boxplot(ratingsByMonth~genres, data=MonthGenre, ylab="RatingScore/Month",las=2, main="Average Rating Score by Month",ylim=c(1,5))


WeekGenre=GenreMerge%>%
  group_by(genres,Week)%>%
  summarise(ratingsByWeek=mean(ratings))

ggplot(data = WeekGenre, aes(x =genres , y = ratingsByWeek, color = Week)) +       
  geom_line(aes(group = Week)) + geom_point()+
  theme(panel.background = element_blank())+labs(caption = "")


plot(ratingsByWeek~genres, data=WeekGenre, ylab="RatingScore/Week",las=2, main="Average Rating Score by Week",ylim=c(1,5))
```















Movies database Growth
```{r}
# Movies Database Growth

uniqueMovies=data_moviesRatings[!duplicated(data_moviesRatings[1]),]
uniqueMovies=uniqueMovies[order(as.Date(uniqueMovies$timestamp, format="%d/%m/%Y")),]
for (i in 1:length(uniqueMovies$timestamp)) {
  uniqueMovies$diff[i]<-round(interval(uniqueMovies$timestamp[[1]],uniqueMovies$timestamp[[i]])/ddays(1), digits = 0)
}

uniqueMovies$daysDiff=c(0, diff(uniqueMovies$diff))
uniqueMovies$cumMovieDays = cumsum(uniqueMovies$daysDiff)
uniqueMovies$Seq<-seq.int(nrow(uniqueMovies))

moviesDatabase=uniqueMovies%>%
  group_by(cumMovieDays)%>%
  summarise(moviesAdded = length(movieId))%>%
  transform(cumMovies = cumsum(moviesAdded))

  # Plot movies database growth over days
    ggplot(moviesDatabase,
          aes(cumMovieDays,cumMovies)) + 
          geom_line() +
          theme(panel.background = element_blank())+
          ylim(c(1,10000))+
          xlim(c(1,8000))+
          xlab("Days Passed") +
          ylab("Movies Added / Movie database growth") +
          ggtitle("Movies database growth from 1995 to 2016") +labs(caption = "b) Movies database growth")
    
          # Plot new users per day
    ggplot(usersDatabase,
          aes(cumUserDays,moviesAdded)) + 
          geom_line() +
          theme(panel.background = element_blank())+

          xlab("Days Passed") +
          ylab("Users Added") +
          ggtitle("Users database growth from 1995 to 2016") +labs(caption = "a) Users database growth")

```
Users Database Growth

```{r}
    
# Users Database Growth

uniqueUsers=data_moviesRatings[!duplicated(data_moviesRatings[4]),]
uniqueUsers=uniqueUsers[order(as.Date(uniqueUsers$timestamp, format="%d/%m/%Y")),]
for (i in 1:length(uniqueUsers$timestamp)) {
  uniqueUsers$diff[i]<-round(interval(uniqueUsers$timestamp[[1]],uniqueUsers$timestamp[[i]])/ddays(1), digits = 0)
}

uniqueUsers$daysDiff=c(0, diff(uniqueUsers$diff))
uniqueUsers$cumUserDays = cumsum(uniqueUsers$daysDiff)

usersDatabase=uniqueUsers%>%
  group_by(cumUserDays)%>%
  summarise(usersAdded = length(movieId))%>%
  transform(cumUsers = cumsum(usersAdded))

  # Plot users database growth over days
    ggplot(usersDatabase,
          aes(cumUserDays,cumUsers)) + 
          geom_line() +
          theme(panel.background = element_blank())+
          ylim(c(1,800))+
          xlim(c(1,8000))+
          xlab("Days Passed") +
          ylab("Users Added / User database growth") +
          ggtitle("Users database growth from 1995 to 2016") +labs(caption = "a) Users database growth")
    
      # Plot new users per day
    ggplot(usersDatabase,
          aes(cumUserDays,usersAdded)) + 
          geom_line() +
          theme(panel.background = element_blank())+

          xlab("Days Passed") +
          ylab("Users Added") +
          ggtitle("Users database growth from 1995 to 2016") +labs(caption = "a) Users database growth")

```

    




